---
title: "HW4"
author: "Kade Spaulding"
date: "2026-09-23"
output: pdf_document
---
## 1. 
```{r}
source("C:/Users/kmsp240/Downloads/HW2_KS.R")
```

## 2. 
### a. For one game
```{r}
card <- createBingo()

called_numbers <- sample(1:75, 75)

marked <- matrix(0, nrow=5, ncol=5)
marked[3,3] <- 1

for (i in 1:75){
  
  marked <- markBingo(card, marked, called_numbers[i])
  
  win_type <- checkBingo(marked)
  
  if (length(win_type) > 0){
    break
  }
}

win_type
i
```
### b. for 25 games
```{r}
win_types1 <- c()

for (game in 1:25) {
  
  card <- createBingo()
  
  called_numbers <- sample(1:75, 75)
  
  marked <- matrix(0, nrow=5, ncol=5)
  marked[3,3] <- 1
  
  for (i in 1:75) {
    
    marked <- markBingo(card, marked, called_numbers[i])
    
    win_type1 <- checkBingo(marked)
    
    if (length(win_type1) > 0) {
      break
    }
  }
  
  win_types1 <- c(win_types1, win_type1)
}

barplot(table(win_types1),
        main = "Frequency of Bingo Win Types for 25 games",
        ylab = "Number of Games")


win_types2 <- c()

for (game in 1:50) {
  
  card2 <- createBingo()
  
  called_numbers2 <- sample(1:75, 75)
  
  marked2 <- matrix(0, nrow=5, ncol=5)
  marked2[3,3] <- 1
  
  for (i in 1:75) {
    
    marked2 <- markBingo(card2, marked2, called_numbers2[i])
    
    win_type2 <- checkBingo(marked2)
    
    if (length(win_type2) > 0) {
      break
    }
  }
  
  win_types2 <- c(win_types2, win_type2)
}

barplot(table(win_types2),
        main = "Frequency of Bingo Win Types for 50 games",
        ylab = "Number of Games")

win_types3 <- c()
for (game in 1:100) {
  
  card3 <- createBingo()
  
  called_numbers3 <- sample(1:75, 75)
  
  marked3 <- matrix(0, nrow=5, ncol=5)
  marked3[3,3] <- 1
  
  for (i in 1:75) {
    
    marked3 <- markBingo(card3, marked3, called_numbers3[i])
    
    win_type3 <- checkBingo(marked3)
    
    if (length(win_type3) > 0) {
      break
    }
  }
  
  win_types3 <- c(win_types3, win_type3)
}

barplot(table(win_types3),
        main = "Frequency of Bingo Win Types for 100 games",
        ylab = "Number of Games")


win_types4 <- c()
for (game in 1:100) {
  
  card4 <- createBingo()
  
  called_numbers4 <- sample(1:75, 75)
  
  marked4 <- matrix(0, nrow=5, ncol=5)
  marked4[3,3] <- 1
  
  for (i in 1:75) {
    
    marked4 <- markBingo(card4, marked4, called_numbers4[i])
    
    win_type4 <- checkBingo(marked4)
    
    if (length(win_type4) > 0) {
      break
    }
  }
  
  win_types4 <- c(win_types4, win_type4)
}

barplot(table(win_types4),
        main = "Frequency of Bingo Win Types for 1000 games",
        ylab = "Number of Games")
```
It seems that column and row wins are relatively equal across simulations, with diagonal being lower than both by quite a large amount. Intuitively this makes sense, as there are 5 different ways to win with a column or row, as opposed to the two ways to win with diagonals

## 3. 
```{r}
win_types4 <- c()
numbers_called <- c()
for (game in 1:100) {
  
  card4 <- createBingo()
  
  called_numbers4 <- sample(1:75, 75)
  
  marked4 <- matrix(0, nrow=5, ncol=5)
  marked4[3,3] <- 1
  
  for (i in 1:75) {
    
    marked4 <- markBingo(card4, marked4, called_numbers4[i])
    
    win_type4 <- checkBingo(marked4)
    
    if (length(win_type4) > 0) {
      break
    }
  }
  
  win_types4 <- c(win_types4, win_type4)
  numbers_called <- c(numbers_called, rep(i, length(win_type4)))
}

tapply(numbers_called, win_types4, mean)
```
Diagonal has a free space so one less number needs to be called to have a win.
