---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
## 1. 

### 1. 
```{r}
numerical_estimate <- function(f,a,b,n, rule){
    if (rule == "rectangle"){
      h <- (b-a)/n
      x1 <- seq(a, b-h, length.out = n)
      estimate <- h * sum(f(x1))
      return(estimate)} 
    if (rule == "trapezoid"){
      h <- (b-a)/n
      x2 <- seq(a, b, length.out = n+1)
      estimate <- (h/2)*((f(a) + (2*sum(f(x2[-c(1,n+1)]))) + f(b)))
      return(estimate)
    } 
    if (rule == "simpsons"){
      h <- (b-a)/n
      x3 <- seq(a, b, length.out = n+1)
      x4 <- x3[seq(2, n, by = 2)]  # weight 4
      if (n == 2) {
        x5 <- numeric(0)
        } else {
        x5 <- x3[seq(3, n, by = 2)]
        }
      estimate <- (h/3) * (f(a) + (4*sum(f(x4))) + (2*sum(f(x5))) + f(b))
      return(estimate)
    }
}


```
### 2. 
By hand the rectangle rule should be $$ 1 * e^0 = 1 $$ the trapezoidal rule should be $$ \frac{1}{2}*(e^0 + e^1) = \frac{1+e}{2} = 1.859$$ and the Simpsons rule requires even number of sub intervals, so I will not do that by hand. Yes my function matches these values
```{r}
f_x <- function(x){
  exp(x)
}
numerical_estimate(f_x,0,1,1,"rectangle") # 1
numerical_estimate(f_x,0,1,1,"trapezoid") # 1.859
#numerical_estimate(f_x,0,1,1,"simpsons") # error because of Simpsons rule requirement
```

### 3. 
By hand the rectangle rule should be $$\frac{1}{2}*(e^0 + e^.5) = 1.324$$  the trapezoidal rule should be $$\frac{1}{4} * (e^0 + 2*e^.5 + e^1) = 1.754$$ and simpsons rule should be $$ \frac{1}{6} * (e^0 + 4*e^.5 + e^1) = 1.718=9$$ Yes my functions match
```{r}
numerical_estimate(f_x,0,1,2,"rectangle") # 1.324
numerical_estimate(f_x,0,1,2,"trapezoid") # 1.754
numerical_estimate(f_x,0,1,2,"simpsons") # 1.719
```

### 4. 
Since simpsons method requires even subintervals the error did not do much better than other methods with 2n. However, when n=10 the error is extremely close to 0 and performs much better than the other two methods with that many subintervals. 
```{r}
actual <- integrate(f_x, 0,1)$value
actual #1.718282

#for n = 5
rectangular5 <- numerical_estimate(f_x,0,1,5,"rectangle")
trapezoidal5 <- numerical_estimate(f_x,0,1,5,"trapezoid")
simpsons5 <- numerical_estimate(f_x,0,1,5,"simpsons") #not even, invalid

error_rectangular5 <- actual - rectangular5
error_trapezoidal5 <- actual - trapezoidal5
error_simpsons5 <- actual - simpsons5

error_rectangular5 # .166
error_trapezoidal5 #-0.006
error_simpsons5 #.163


#for n = 10
rectangular10 <- numerical_estimate(f_x,0,1,10,"rectangle")
trapezoidal10 <- numerical_estimate(f_x,0,1,10,"trapezoid")
simpsons10 <- numerical_estimate(f_x,0,1,10,"simpsons") 

error_rectangular10 <- actual - rectangular10
error_trapezoidal10 <- actual - trapezoidal10
error_simpsons10 <- actual - simpsons10

error_rectangular10 #0.08
error_trapezoidal10 # - 0.001
error_simpsons10 #-9.534658e-07
```

## GAMMA Function
### 1. 
```{r}
gamma_function <- function(a, x){
  (x^(a-1))*exp(-x)
}
library(ggplot2)

x <- seq(0.01, 10, length.out = 1000)

data <- data.frame(
  x = x,
  alpha1 = gamma_function(1, x),
  alpha2 = gamma_function(2, x)
)

ggplot(data, aes(x = x)) +
  geom_line(aes(y = alpha1)) +
  geom_line(aes(y = alpha2))

```

### 2. 
When alpha equals one the function becomes $$ \int_{0}^{\infty} e^{-x} dx$$ which becomes 
$$-e^{-x}$$ evaluated from 0 to infinity => $$-e^{-\infty} - (-e^0)$$ which is $$0 - (-1)$$ so the solution is 1. 

### 3. 
```{r}
gamma1 <- function(x) {
  gamma_function(1, x)
}
numerical_estimate(gamma1, 0, 10, 3, "trapezoid") #1.79

```

### 4. 
I kept trying larger and larger and it is not getting more accurate than 1.081977
```{r}
numerical_estimate(gamma1, 0, 100000, 100000, "trapezoid") 
```

### 5. 
The integrals go up by multplying sequentially by n-1
```{r}
gamma2 <- function(x) {
  gamma_function(2, x)
}
numerical_estimate(gamma2, 0, 100000, 100000, "trapezoid") #around 1

gamma3 <- function(x) {
  gamma_function(3, x)
}
numerical_estimate(gamma3, 0, 100000, 100000, "trapezoid") #around 2

gamma4 <- function(x) {
  gamma_function(4, x)
}
numerical_estimate(gamma4, 0, 100000, 100000, "trapezoid") #around 6

gamma5 <- function(x) {
  gamma_function(5, x)
}
numerical_estimate(gamma5, 0, 100000, 100000, "trapezoid") #around 24


```
