---
title: "Lab 5"
author: "Kade Spaulding"
date: "2026-09-17"
output: html_document
---
1.
```{r}
x <- sample(1:365, 25, replace = TRUE)

any(duplicated(x))#False, so none the same
```

2.
```{r}
genRoom <- function(n.indiv){
  x <- sample(1:365, n.indiv, replace = TRUE)
  if (any(duplicated(x))){
    print("There is a shared birthday")
  } else {
    print("There is no shared birthday")
  }
}
```

3.  
```{r}
#a. elapsed was 0.00
system.time({
  rooms <- matrix(NA, nrow=1000, ncol=25)

  for (i in 1:1000){
    rooms[i,] <- sample(1:365, 25, replace = TRUE)
  }
})

#b. elasped was 0.02
system.time({
  rooms2 <- t(sapply(1:1000, function(i) sample(1:365, 25, replace = TRUE)))
})

```
c. The preallocated one with the for loop took less time according to system.time. I would guess the apply function would take a similar amount of time, as the two were only 2 hundreths of a second off 
4.
```{r}
simRooms <- function(n.indiv, n.sim){
    rooms <- matrix(NA, nrow=n.sim, ncol=n.indiv)
    no_shared <- 0
    
    for (i in 1:n.sim){
      rooms[i,] <- sample(1:365, n.indiv, replace = TRUE)
    
      
    
      if (!any(duplicated(rooms[i,]))) {
      no_shared <- no_shared + 1}}
    
    return(no_shared/n.sim)
}

n <- seq(2, 60, by = 2)

prob <- sapply(n, function(x) simRooms(x, 1000))
```

5. As the room gets larger the probability of no shared birthdays gets smaller, which is what I would expect.
```{r}
results <- data.frame(n, prob)
library(ggplot2)

ggplot(results, aes(x = n, y = prob)) +
      geom_point() +
      geom_line() +
      labs(
      title = "Probability of No Shared Birthdays by Room Size",
      x = "Number of Individuals",
      y = "Probability of No Shared Birthdays"
  )

```

6. We find the same thing across multiple simulations, with the probability decreasing with number of people in a room increasing, thought the smaller simulations are a little less of a smooth decrease.
```{r}
n2 <- c(50,100,500,1000,5000)
results2 <- data.frame()

for (i in n2) {
  prob2 <- sapply(n, function(x) simRooms(x, i))
  
  temp <- data.frame(
    n,
    i,
    prob2
  )
  
  results2 <- rbind(results2, temp)
}

ggplot(results2, aes(x = n, y = prob2, color = factor(i))) +
  geom_point() +
  geom_line() +
  labs(
    title = "Probability of No Shared Birthdays by Room Size",
    x = "Number of Individuals",
    y = "Probability of No Shared Birthdays",
    color = "Number of Rooms Simulated"
  )
```
